---
title: "HW3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
library(knitr)
library(effsize)
library(car)
library(RColorBrewer)
library(ggplot2)

survey <- read_csv("//esm.ucsb.edu/mesm/co2019/jvazin/Desktop/HW3Data (2).csv")

```

Question 1- Regression

```{r}
summary(survey)

#Relevel the factors
survey$income<-as.factor(survey$income)
survey$income<-relevel(survey$income, ref="poor")
survey$age<-as.factor(survey$age)
survey$age<-relevel(survey$age, ref="tothirty")

#GLM
surveySB<-glm(vote~risk+bid+NEP+income+age, data=survey)
surveySB
summary(surveySB)

#Table- already did stargazer so don't need 
coeff<-coefficients(surveySB)
coeff
cdf<-as.data.frame(rbind(coeff))
str(cdf)
colnames(cdf)
colnames(cdf)<-c("C", "RR", "P", "NEP", "IM", "IOP", "IR", "IVR", "over60", "To50", "To40", "To60")
cdf


```

Question 2 - Value of Single Whale Death
```{r}

#4% RR is 1 whale death, what is the value of that compared to the baseline?

#predict vote values
predictvote<-predict(surveySB)
surveypredict<-cbind(survey, predictvote)

#populate predicted bids for 4% RR
survey4<-surveypredict
survey4$risk<-4
Bid4<-(cdf$C+
        (cdf$RR*survey4$risk)+
        (cdf$NEP*survey4$NEP)+
        ifelse(survey4$income=="middle", cdf$IM, 0)+
        ifelse(survey4$income=="rich", cdf$IR, 0)+
        ifelse(survey4$income=="very_rich", cdf$IVR, 0)+
        ifelse(survey4$income=="one_percent", cdf$IOP, 0)+
        ifelse(survey4$age=="tofifty", cdf$To50, 0)+
        ifelse(survey4$age=="toforty", cdf$To40, 0)+
        ifelse(survey4$age=="tosixty", cdf$To60, 0)+
        ifelse(survey4$age=="oversixty", cdf$over60, 0)-
        0.5)/-cdf$P


WTP4<-cbind(survey4,Bid4)
WTP4

#populate predicted bid for Basline
survey0<-surveypredict
survey0$risk<-0
Bid0<-(cdf$C+
        (cdf$RR*survey0$risk)+
        (cdf$NEP*survey0$NEP)+
        ifelse(survey0$income=="middle", cdf$IM, 0)+
        ifelse(survey0$income=="rich", cdf$IR, 0)+
        ifelse(survey0$income=="very_rich", cdf$IVR, 0)+
        ifelse(survey0$income=="one_percent", cdf$IOP, 0)+
        ifelse(survey0$age=="tofifty", cdf$To50, 0)+
        ifelse(survey0$age=="toforty", cdf$To40, 0)+
        ifelse(survey0$age=="tosixty", cdf$To60, 0)+
        ifelse(survey0$age=="oversixty", cdf$over60, 0)-
        0.5)/-cdf$P

WTP04<-cbind(WTP4, Bid0)
WTP04

#Value of One Whale
WTP04$onewhale<-WTP04$Bid4-WTP04$Bid0


```

Bid Equation
Bid= (Everything-Vote)/0.0011

**Equation**: Bid=((0.1429+0.0007(risk)+0.0159(NEP)-0.0027(incomemiddle)+0.0048(incomerich)+0.0441(incomevery_rich)+0.0061(incomeone_percent)-0.0105(agetofifty)-0.0401(agetoforty)-0.0367(agetosixty)-0.0204(ageoversixty)) - Vote) / 0.0011

Question 3

```{r}

survey60<-surveypredict
survey60$risk<-60
Bid<-(cdf$C+
        (cdf$RR*survey60$risk)+
        (cdf$NEP*survey60$NEP)+
        ifelse(survey60$income=="middle", cdf$IM, 0)+
        ifelse(survey60$income=="rich", cdf$IR, 0)+
        ifelse(survey60$income=="very_rich", cdf$IVR, 0)+
        ifelse(survey60$income=="one_percent", cdf$IOP, 0)+
        ifelse(survey60$age=="tofifty", cdf$To50, 0)+
        ifelse(survey60$age=="toforty", cdf$To40, 0)+
        ifelse(survey60$age=="tosixty", cdf$To60, 0)+
        ifelse(survey60$age=="oversixty", cdf$over60, 0)-
        0.5)/-cdf$P

WTP<-round(Bid, 2)
WTP60<-cbind(survey60,WTP)
WTP60

```


Question 5 & 6
```{r}
TWTP<-mean(WTP60$WTP)*150000
TC<-150000*60
CS<-TWTP-TC
NB<-CS-7000000

mean(WTP60$WTP)
TWTP
TC
CS
NB

```

```{r}
#Overall Benefit does not outweight cost- Why?

ggplot(data=WTP60)+
  geom_point(aes(x=predictvote, y=WTP, colour=NEP))+
  scale_colour_gradient(high = "#FF3300", low = "#FFCC00")

#Since NEP was a large predictor of YES response, how does it effect WTP? At what WTP would SB residents be likely to vote YES? (The value where p > .5, looks like about 200)

orderWTP<-WTP60[order(-WTP),] 
surveypeople<-seq(1, 500, by=1)
orderWTP$Number<-surveypeople
orderWTP$Proportion<-surveypeople/500


ggplot(data=orderWTP, aes(x = Proportion, y = WTP))+
  geom_point(aes(x=Proportion, y=WTP, colour=NEP))+
  scale_colour_gradient(high = "#FF3300", low = "#FFCC00")+
  geom_smooth(method = "lm", se = FALSE, color="black")




```


Question 7

Risk Reduction=60% RRCost=$1000 Benefit=(20 fewer tons CO2- each transit)
Carbon Credit $Z per ton, need to incentivize 

If each shipper reduces by 20 tons, recieve $Z per ton*20 tons


20*Z=1000
Z*=1000/20
Z*= $50 per ton

*$50 per ton*

Question 8

Z*=$50 per ton
Ships have costs equal to their benefits- so their net benefits are $0

60% reduction is about 15 whales

Social value is TWTP the was calculated before ~ $40,013,073

SB residents willing to pay this much for 60% reduction

If voluntary speed reduction, all VSR costs are zero
consumer surplus= TWTP and PS=0 
Total social benefits = CS + PS = *$40,013,073*

